intRo

### 2016-06-23 user-2016/index.Rmd
cut some things per @erichare suggestions

 - Storing the user's results
 - Presenting only relevant options to the user
 - Producing clean and executable R code

## Storing results
 - Users must be able to print results, but only the results they want
 - Reactivity makes this somewhat challenging

**Solution**: Store Buttons

<img src="images/store.png" height="300"></img>

## Storing results (Cont'd)
 - Each module contains, at the bottom, a Store button
 - When Store is pressed, code is stored in code panel
     - Additional challenge: All options selected must also be stored!
 - When user goes to print results, only this particular code is executed

@@

 - Each call is wrapped in a function called `interpolate` [@interpolate]
    - Executes the given R code on the server
    - Writes the code executed to the script window at the bottom of intRo

```{r, eval=FALSE}
nonparametric_test <- function(intro.data, x, y, ...) {
  interpolate(~(wilcox.test(x = df$x, 
                            y = df$y, ...),
                  df = quote(intro.data),
                  x = x,
                  y = y,
                  ...,  
                  `_env` = environment(), 
                  file = "code_nonparametric.R")
}
```

@@

## Server load
Limited testing has been done to assess how `intRo` handles heavy user load

 - Dozens of students accessing app at once
 - Simultaneous larger computations like printing results

More server resources may need to be devoted to handle this, particularly if `intRo` is more widely adopted

>>>>

 - Presenting only relevant options to the user
 - Producing clean and executable R code

@@

 - Each call is wrapped in a function called `interpolate`
    - Executes the given R code on the server
    - Writes the code executed to the script window at the bottom of intRo

```{r, eval=FALSE}
nonparametric_test <- function(intro.data, x, y, ...) {
  ### <b>
  interpolate(~(wilcox.test(x = df$x, 
  ### </b>
                            y = df$y, ...),
                  df = quote(intro.data),
                  x = x,
                  y = y,
                  ...,  
                  `_env` = environment(), 
                  file = "code_nonparametric.R")
}
```

@@
